\documentclass[a4paper,11pt]{simpleresume}
\begin{document}

\name{Sameer Kumar Mishra}
\contact{7204128890}{sameermishravats@gmail.com}{Bangalore}

\section{Work}
\datedsubsection{Amazon Inc.}{January 2018--Present}
SDE-II, External Fulfilment Platform.
\datedsubsection{Samsung Electronics}{July 2014--December 2018}
Software Engineer, Modem Group.

\section{Education}
\datedsubsection{National Institute of Technology, Surathkal}{July 2011--June 2014}
Masters in Computer Application, 8.45 CGPA.
\datedsubsection{St. Xavier's College, Ranchi}{June 2008--May 2011}
B.Sc. Computer Applications, 8.64 CGPA.

\section{Projects}
\datedsubsection{Push Notification for Shipment Lifecycle}{Amazon}
\begin{itemize}
\item Aspect based system for sending push notification whenever a shipment changes state.
\item Dependent teams build dashboards over this notification stream.
\item This helps dependent teams isolate shipments related problems. 
\item Technology used: Amazon SNS, Java, AspectJ.
\end{itemize}
\datedsubsection{Interpreter For Modem Log Query Language}{Samsung}
\begin{itemize}
    \item Developed a Domain Specific Language (DSL) and its interpreter to query modem logs.
    \item 2000+ scripts written in this DSL which save hours of log analysis time per day of test engineers.
    \item Used by 100+ engineers in Samsung Bangalore and Samsung HQ.
    \item Technology used: C++, Boost::Spirit library.
    \end{itemize}
\datedsubsection{Handwritten Digit Recognization}{Hobby Project}
\begin{itemize}
    \item Implemented Neural Network using Stochastic Gradient Descent.
    \item Achieved 96\% accuracy on MNIST dataset.
    \item Github: https://github.com/sameerkrmishra/mnist
    \item Technology used: Python, NumPy.
\end{itemize}
\datedsubsection{Image Classification}{Hobby Project}
\begin{itemize}
    \item Implemented using Convolutional Neural Network.
    \item Trained on images of cats and dogs from Kaggle.
    \item Achieved 90\% accuracy on cross-validation set.
    \item Github: https://github.com/sameerkrmishra/ml- notebooks/blob/master/dogs-and-cats.ipynb
    \item Technology used: Python, Keras, NumPy.
\end{itemize}
\datedsubsection{DB Migration Of A Core Application}{Amazon}
\begin{itemize}
    \item Migrated a core application of the team from one relational DB to another.
    \item Made application code generic in terms of which underlying relational DB is used.
    \item Migrated all the business related DB triggers from the old DB to the new DB.
\end{itemize}
\datedsubsection{New Column In All DB Tables}{Amazon}
\begin{itemize}
    \item Made code changes to populate the new column.
    \item Performed DB backfill to add values in the new column.
\end{itemize}
\datedsubsection{Test Script Generator}{Samsung}
\begin{itemize}
    \item Developed a tool to generate test scripts to mimic scenario from modem logs.
    \item Saved around an hour of effort per testscripts.
    \item Technology used: Python 3.
\end{itemize}

\end{document}
